\documentclass[11pt]{article}

\usepackage{multicol, enumitem}

\input{structure.tex}

\hypersetup{
	pdftitle={Gal Raz - Curriculum vitae},
	pdfauthor={Gal Raz},
    colorlinks=true,
    linkcolor=blue!50!black,
    urlcolor=blue!50!black,
    pdfborderstyle={/S/U/W 1}
}

\begin{document}

\begin{center}
{\huge\bfseries{GAL  RAZ}}

\vspace{0.3cm}

\href{mailto:galraz@gmail.com}{galraz@gmail.com} \quad $\mid$ \quad \href{https://galraz.github.io}{galraz.github.io} \quad $\mid$ \quad \href{https://www.linkedin.com/in/gal-raz-phd-0796aab4/}{LinkedIn}
\end{center}

\vspace*{-0.3cm}

\begin{center}
{\large\bfseries PROFESSIONAL SUMMARY}
\end{center}
\vspace{-0.2cm}

Cognitive scientist (Ph.D., MIT) working at the intersection of research, open scientific tooling, and applied institution-building. Currently Scientific Director of Dabtong House in Bhutan and a researcher at the Henkaku Center in Japan, with prior project leadership at the Gelephu Mindfulness City.

\section*{WORK EXPERIENCE}

\years{\normalsize{2026-present}} \textbf{Founder \& Scientific Director, Dabtong House, Bhutan}
  \vspace{-0.2cm}
\begin{itemize}[itemsep=1pt]
    \item Founded a non-profit that funds and coordinates projects in Bhutan spanning AI, space research, novel construction methods and traditional craft
\end{itemize}

\years{\normalsize{2024-present}} \textbf{Researcher, Henkaku Center, Chiba Institute of Technology, Japan}
  \vspace{-0.2cm}
\begin{itemize}[itemsep=1pt]
    \item Leading research collaborations between Chiba Institute of Technology and Bhutan's sovereign wealth fund and government technology agencies
    \item Integrating AI tooling into Chiba Tech's curricula with industry partners
\end{itemize}

\years{\normalsize{2024-2026}} \textbf{Project Manager, Gelephu Mindfulness City, Bhutan}
  \vspace{-0.2cm}
\begin{itemize}[itemsep=1pt]
    \item Founding member of the Gelephu Mindfulness City ("GMC") team, an autonomous Special Administrative Region in southern Bhutan led by His Majesty the King, building an economic hub that measures success with Gross National Happiness
    \item Set up a corporate registry with lawyers, tax experts and engineers, onboarding the first \textasciitilde50 companies; migrated thousands of businesses into GMC's independent registry, tax, and customs framework
    \item Researched and implemented policy on commercial company matters, land ownership and digital assets
\end{itemize}

\years{\normalsize{2024-2025}} \textbf{Visiting Scientist, Brain \& Cognitive Sciences, MIT} (Part-time)
  \vspace{-0.2cm}
\begin{itemize}[itemsep=1pt]
    \item Advised on and extended software built during PhD; studied function learning in infants and toddlers (PI: Prof. Laura Schulz)
\end{itemize}

\years{\normalsize{2019-2024}} \textbf{PhD Student, Brain \& Cognitive Sciences, MIT}
  \vspace{-0.2cm}
\begin{itemize}[itemsep=1pt]
    \item Devised an automated pipeline for collecting infant behavioral data, a 15x speed-up over traditional methods, collecting data from >700 infants
    \item Developed a rational choice model of attention (optimal decision theory + Bayesian inference), resulting in three first-author publications
    \item Core member of the ManyBabies 2 and ManyBabies 5 analysis teams, organizing a consortium of labs to replicate key results in Theory of Mind and attentional preferences
    \item Supervised 12 undergraduate and Masters students; Head TA for "Infant and Early Childhood Cognition"
\end{itemize}

\section*{EDUCATION}

\years{\normalsize{2024}} \textbf{PhD} in Brain \& Cognitive Sciences (\textit{4.0 GPA}), MIT \\
\years{\normalsize{2018}} \textbf{MSc} in Psychological Research (\textit{with distinction}), University of Oxford \\
\years{\normalsize{2016}} \textbf{BSc} (Hons.) in Liberal Arts and Sciences (\textit{summa cum laude}), University College Utrecht

\section*{AWARDS}

\years{\normalsize{2024}} Best Paper in Developmental Psychology, American Psychological Association

\years{\normalsize{2022-2024}} ICoN Graduate Fellowship

\years{\normalsize{2021}} Walle Nauta Award for Excellence in Undergraduate Teaching

\years{\normalsize{2020}} Cheng Graduate Fellowship

\years{\normalsize{2018}} Humphrey Prize for Best Research Project Dissertation in MSc cohort

\years{\normalsize{2017}} Full scholarship for MSc studies by German Academic Exchange Services

\years{\normalsize{2016}} Kupcinet-Getz Scholar at Weizmann Institute of Science

\section*{SELECTED PUBLICATIONS (full list on \href{https://scholar.google.com/citations?user=kL4kXcEAAAAJ&hl=en}{Google Scholar})}

ManyBabies 5 Consortium (in prep). A large-scale investigation of the proposed shift from familiarity to novelty preference in infant looking time.

\smallbreak

ManyBabies 2 Consortium (under review). Action anticipation based on an agent's epistemic state in toddlers and adults.

\smallbreak

\textbf{Raz, G.}*, Cao, A.*, Saxe, R., \& Frank, M.C. (2025). A stimulus-computable rational model of habituation in infants and adults. \textit{eLife} (*equal contribution)

\smallbreak

\textbf{Raz, G.}, Piccolo, S., Medrano, J., Liu, S., Lydic, K., et al. (2024). An asynchronous, hands-off workflow for looking time experiments with infants. \textit{Developmental Psychology} (Editor's Choice Award)

\smallbreak

\textbf{Raz, G.} \& Saxe, R. (2020). Learning in Infancy Is Active, Endogenously Motivated, and Depends on the Prefrontal Cortices. \textit{Annual Review of Developmental Psychology}, 2, 247-268.

\section*{COMMUNITY SERVICE AND OUTREACH}

\years{\normalsize{2017 - present}} Volunteer at Dhamma Meditation Centers — serve at 10-day silent retreats (Germany, Israel, UK); lead teams of 8-10 cooking for 100-200 meditators. \\
\years{\normalsize{2020 - 2024}} Graduate Student Council, MIT School of Science — advised the Dean's office; implemented an internship policy and relocation stipend for incoming graduates. \\
\years{\normalsize{2017}} English \& Math teacher, Lamdon Jamyang School, Ladakh — 6-month placement teaching children aged 6-13 in northern India.

\section*{MISCELLANEOUS SKILLS AND EXPERIENCES}

\textbf{Languages}: German, English and Hebrew (fluent), Spanish (level B2), Korean (A1) \smallbreak

\textbf{Programming languages (in order of proficiency)}: Python, R, Stan, MATLAB, JavaScript, Unity scripting (C\#), WebPPL \smallbreak

\textbf{Teaching Certifications:} Graduate Teaching Certificate @ MIT Teaching + Learning Lab, TEFL Certificate (120-hour course for teaching English as a foreign language) \smallbreak

\textbf{For fun}: Vipassana meditation, Judo, Yoga, chess, poker, RTS games, electronic music \smallbreak

\vfill % Whitespace before final footer

%----------------------------------------------------------------------------------------
%	FINAL FOOTER
%----------------------------------------------------------------------------------------

% Any final footer text such as a URL to the latest version of this CV, last updated date, compiled in XeTeX, etc
%

%----------------------------------------------------------------------------------------

\end{document}